---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

*NSTI_for_KL* has all the demographic, cost, and insurance data. 

_________________________________________________________

**"Total Cost"** is what we are interested in as outcome.  

**Goal** is to determine whether there are characteristics that predict who will cost the most (top quartile). 

*NSTI_meds_for_KL* has all the medications. 
- which patients got which antibiotics for how long
- when they were started, changed, and stopped in relationship to admission and last OR visit.

*NSTI_debride_for_KL* gives list of OR visits 



```{r echo = FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(stats)
library(plyr)
require(data.table)
library(tidyr)
library(dplyr)

#change to your directory when running
path <- "C:/Users/Kevin/Documents/GitHub/NSTI_harborview"
setwd(path)


# Importing dataset
nsti <- data.frame(fread("~/NSTI_for_KL.csv", header = TRUE))
nsti_debrid <- data.frame(fread("~/NSTI_debride_for_KL.csv", header = TRUE))
nsti_Meds <- data.frame(fread("~/NSTI_meds_for_KL.csv",header = TRUE))

```

**Variables**(nsti: 78 variables)

**Numerical**

- Patient, Age, Race
- Discharge Date
- Outcome?? (categorical)
- Admit date (x /y??)
- ICU los??, ICU hours (num)
- Hosp los?? (num)
- Vent Days(num) 
- DC dispo (categorical)
- Mech of infection (categorical)

**Categorical**

- Comorbid codes (Categorical seperated by ";")
- co.morbids (numerical)
- location code 1,2 (categorical, only on some patients)
- ICD 10 code & description / ICD 10 2 missing?? 
- Region (categorical)
- debirdment count (numerical - int)
- direct cost days? (only on some patients)
- direct/indirect cost/total cost (numerical)
- direct cost index / pb hmc (direct/inndirect/total cost) / pb uwp gross charges / cost allocation (only on some patients )

- Vent free days (numerical)

- insurance & type (categorical)


**Binary**

- Transfer (binary)
- **transfer** duplicate 
- Debridement
- Ards, arf cauti, cdiff, clabsi, cva, cpr, decub, dvt, unplanned (ett & or), mi, pe, sepsis, vap, withdrawl, bleeding, chf, cirr, crf, cva, dm, dementia, drug abuse, etoh abuse, htn, MI, resp, smoker, amputation
- death 
- is female
- highest quartile cost 
- public/private/uninsured insurance
- other??

Questions: Why some features aren't on all patients 


```{r}
head(nsti)
summary(nsti)
```

Things I need to fix 
- SEX binary 
- discharge, admit x/y 
- death, is female, transfer is considered a numerical vs binary 

NA 
- Some features have emtpy strings instead for missing values 
- Others have NA's this usally starts when we get to PB costs 

```{r}
#removing the duplicate transfer binary 
nsti <- subset(nsti, select = -c(TRANSFER,OUTCOME, isFemale))
```

```{r}
#converting character to date data format
dates = c("Discharge", "Admit.x", "Admit.y")
nsti[dates] <- lapply(nsti[dates], function(x) as.Date(x, "%m/%d/%Y"))
```
```{r}
#replacing NOT in race to NA
nsti$RACE[ nsti$RACE == "NOT"] <- NA
```

Converting categorical features to factor

```{r}
cols <- c("SEX", "RACE", "DC.DISPO", "MECHANISM.OF.INFECTION", "LOCATION.CODE.1", "LOCATION.CODE.2", "ICD.10..1.DESCRIPTION", "REGION",
          "Insure_type", "ICD.10.CODE..1")


nsti[cols] <- lapply(nsti[cols], as.factor)
```


```{r}
nsti["CoMorbid.Codes"] <- lapply(nsti["CoMorbid.Codes"], function(x) strsplit(x, ";"))
nsti["Insure"] <- lapply(nsti["Insure"], function(x) strsplit(x, ";"))
nsti["Patient"] <- lapply(nsti["Patient"], function(x) str_sub(x, 1,-6))
```
Region is weird case in which is can have more than one region. Not sure how we want to address this.

Issue with patient 179*NSTI or V1 (70) which has a co.morbids value of asthma 


```{r}
nsti[nsti$V1 == 70,]

```


```{r}
nsti
```

```{r}
ggplot(data = nsti, aes(x = AGE)) +
  geom_bar() + 
   facet_grid(. ~ Death) 
ggplot(data = nsti, aes(x = Indirect.Costs)) +
  geom_bar() 
```

```{r}
nsti$Indirect.Costs
```


```{r}
nsti_debrid
```

```{r}
dates = c("ADMIT.DATE", "DEBRIDE.1.START.DATE", "DEB.2.DATE","DEB3.DATE", "DEB4.DATE", "REC1.DATE", "REC2.DATE", "REC3.DATE", "REC4.DATE", "DC.Date")
nsti_debrid[dates] <- lapply(nsti_debrid[dates], function(x) as.Date(x, "%m/%d/%Y"))

cols <- c("DEB1.CPT", "DEB2.CPT", "DEB3.CPT", "DEB4.CPT", "REC1CPT", "REC1.TOTAL", "REC1.EXP", "REC1.FLAP",
          "REC2.CPT", "REC2.EXP","REC2.FLAP", "Transfer")

nsti_debrid[cols] <- lapply(nsti_debrid[cols], as.factor)
```

```{r}
summary(nsti_debrid)
```

```{r}

dates = c("ADMIT.DATE", "Med.Start.Date")
nsti_Meds[dates] <- lapply(nsti_Meds[dates], function(x) as.Date(x, "%m/%d/%Y"))

cols <- c("Meds", "Med.Location")

nsti_Meds[cols] <- lapply(nsti_Meds[cols], as.factor)


```


```{r}
summary(nsti_Meds)
```

```{r}
test <- merge(nsti,nsti_debrid, by.x = "Patient", by.y = "study_ID")
```

```{r}
test
```


```{r}
ggplot(data = nsti, aes(x = AGE)) +
  geom_bar()
ggplot(data = nsti, aes(x = SEX)) +
  geom_bar()
ggplot(data = nsti, aes(x = OUTCOME)) +
  geom_bar()
ggplot(data = nsti, aes(x = ICD.10..1.DESCRIPTION)) +
  geom_bar()
#summary(nsti_Meds)
```

