---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

*NSTI_for_KL* has all the demographic, cost, and insurance data. 

_________________________________________________________

**"Total Cost"** is what we are interested in as outcome.  

**Goal** is to determine whether there are characteristics that predict who will cost the most (top quartile). 

*NSTI_meds_for_KL* has all the medications. 
- which patients got which antibiotics for how long
- when they were started, changed, and stopped in relationship to admission and last OR visit.

*NSTI_debride_for_KL* gives list of OR visits 



```{r echo = FALSE, message=FALSE}
library(plyr); library(dplyr)
library(tidyverse)
library(ggplot2)
library(stats)

require(data.table)
library(tidyr)
library(chron)
library(lubridate)
library(data.tree)
library(plotly)
library(d3r)
library(htmltools)
library(rhtmlSankeyTree)


#change to your directory when running
#path <- "C:/Users/Kevin Li/Documents"
#setwd(path)

# Importing dataset
nsti <- data.frame(fread("NSTI_for_KL.csv", header = TRUE))
nsti_debrid <- data.frame(fread("NSTI_debride_for_KL.csv", header = TRUE))
nsti_Meds <- data.frame(fread("NSTI_meds_for_KL.csv",header = TRUE))
```


**Variables**(nsti: 78 variables)

**Numerical**

- Patient, Age, Race
- Discharge Date
- Outcome?? (categorical)
- Admit date (x /y??)
- ICU los??, ICU hours (num)
- Hosp los?? (num)
- Vent Days(num) 
- DC dispo (categorical)
- Mech of infection (categorical)

**Categorical**

- Comorbid codes (Categorical seperated by ";")
- co.morbids (numerical)
- location code 1,2 (categorical, only on some patients)
- ICD 10 code & description / ICD 10 2 missing?? 
- Region (categorical)
- debirdment count (numerical - int)
- direct cost days? (only on some patients)
- direct/indirect cost/total cost (numerical)
- direct cost index / pb hmc (direct/inndirect/total cost) / pb uwp gross charges / cost allocation (only on some patients )

- Vent free days (numerical)

- insurance & type (categorical)


**Binary**

- Transfer (binary)
- **transfer** duplicate 
- Debridement
- Ards, arf cauti, cdiff, clabsi, cva, cpr, decub, dvt, unplanned (ett & or), mi, pe, sepsis, vap, withdrawl, bleeding, chf, cirr, crf, cva, dm, dementia, drug abuse, etoh abuse, htn, MI, resp, smoker, amputation
- death 
- is female
- highest quartile cost 
- public/private/uninsured insurance
- other??

Questions: Why some features aren't on all patients 


```{r}
head(nsti)
summary(nsti)
```

Things I need to fix 
- SEX binary 
- discharge, admit x/y 
- death, is female, transfer is considered a numerical vs binary 

NA 
- Some features have emtpy strings instead for missing values 
- Others have NA's this usally starts when we get to PB costs 

```{r}
#removing the duplicate transfer binary 
nsti <- subset(nsti, select = -c(TRANSFER,OUTCOME, isFemale))
```

```{r}
#converting character to date data format
dates = c("Discharge", "Admit.x", "Admit.y")
nsti[dates] <- lapply(nsti[dates], function(x) as.Date(x, "%m/%d/%Y"))

#replacing NOT in race to NA
nsti$RACE[ nsti$RACE == "NOT"] <- NA

#Converting categorical features to factor
cols <- c("SEX", "RACE", "DC.DISPO", "MECHANISM.OF.INFECTION", "LOCATION.CODE.1", "LOCATION.CODE.2", "ICD.10..1.DESCRIPTION", "REGION",
          "Insure_type", "ICD.10.CODE..1")
nsti[cols] <- lapply(nsti[cols], as.factor)

#Splitting features that are bound by semi colons into a list
nsti["CoMorbid.Codes"] <- lapply(nsti["CoMorbid.Codes"], function(x) strsplit(x, ";"))
nsti["Insure"] <- lapply(nsti["Insure"], function(x) strsplit(x, ";"))
nsti["Patient"] <- lapply(nsti["Patient"], function(x) str_sub(x, 1,-6))

```

Region is weird case in which is can have more than one region. Not sure how we want to address this.

Issue with patient 179*NSTI or V1 (70) which has a co.morbids value of asthma 


```{r}
nsti[nsti$V1 == 70,]
```

**Debrid**
Changing the date features that were typed under character to actual date types as posicit as well as features that should be factors as well 

```{r}
#changing to date type
dates = c("ADMIT.DATE", "DEBRIDE.1.START.DATE", "DEB.2.DATE","DEB3.DATE", "DEB4.DATE", "REC1.DATE", "REC2.DATE", "REC3.DATE", "REC4.DATE", "DC.Date")
nsti_debrid[dates] <- lapply(nsti_debrid[dates], function(x) as.Date(x, "%m/%d/%Y"))

#changing to factors 
cols <- c("DEB1.CPT", "DEB2.CPT", "DEB3.CPT", "DEB4.CPT", "REC1CPT", "REC1.TOTAL", "REC1.EXP", "REC1.FLAP",
          "REC2.CPT", "REC2.EXP","REC2.FLAP", "Transfer")
nsti_debrid[cols] <- lapply(nsti_debrid[cols], as.factor)
```

**Meds**
Converting the features to factors 

```{r}
cols <- c("Meds", "Med.Location")
nsti_Meds[cols] <- lapply(nsti_Meds[cols], as.factor)
```

Structuring the time data in medication
```{r}
#creating a new dataframe with only these medications 
nstimeds_new <- data.frame(nsti_Meds[nsti_Meds["Meds"] != c("DOBU", "ENOX", "EPINEP", "NOPRESS", "STERIOD", "VASO", "WARF", 
                                                        "ANTIBIOT", "DOP", "HEP", "IVIG", "NOREPI", "PCC", "SOFA"),])
#removing med location
nstimeds_new <- subset(nstimeds_new, select = -c(Med.Location))

#removing entries that have a NOT date/time or UNK might go back and change if there is an alternative route 
nstimeds_new <- nstimeds_new[nstimeds_new["Med.Start.Date"] != "NOT" & nstimeds_new["Med.Start.Date"] != "UNK" & nstimeds_new["Med.Start.Date"] != "",]


#converting NOT to 0.00 Not a good system need to revise if we are using med location 
nstimeds_new[nstimeds_new == "NOT"] <- "0:00"
nstimeds_new[nstimeds_new == ""]  <- "0:00"
nstimeds_new[nstimeds_new == "UNK"]   <- "0:00"

# removes all na. Need to reassess later for 
nstimeds_new = nstimeds_new[complete.cases(nstimeds_new),]
```

```{r}
#Converting time and date to a new feature with both 
nstimeds_new$totalTime <- strptime(paste(nstimeds_new$Med.Start.Date,nstimeds_new$Med.Start.Time, sep = " "),"%m/%d/%Y %H:%M")
```

```{r}
#merging datasets with medication data
nsti_new <- merge(nsti,nsti_debrid, by.x = "Patient", by.y = "study_ID")
nsti_new <- nsti_new[nsti_new$Minutes.from > 0,]
nsti_new <- nsti_new[complete.cases(nsti_new$Minutes.from),]
#nsti_med_time <- subset(nsti_new, select = c(Patient, Admit.x, medsort,Minutes.from))
```

- Time between admission and last debridement
- Total time each patient received each antibiotic (should be the difference between the first med start date/time until the last med start date/time for each patient--ignore all time points between first and last administration)

- Time between last debridement and last med start date/time for each antibiotic

diff = last medication to first medication
admittilast = minutes from admit to last deb 
debtomed = hours from last med to last deb 

```{r}

medsdf = data.frame(patient = integer(), med = character(), diff = character())


for (i in nsti_new$Patient){
  temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
  meds = strsplit(paste(unique(temp$Meds)), " ")
  debridepatient = nsti_debrid %>% subset(study_ID == i)
  debridedate = strptime(paste(debridepatient$DEBRIDE.1.START.DATE,debridepatient$DEBRIDE.1.START.TIME, sep = " "),"%Y-%m-%d %H:%M") +
                debridepatient$Minutes.from.1st.Deb.to.last*60
  for (y in meds){
    tempmed <- temp[temp$Meds == y,]
    if (nrow(tempmed) >1){
      sortedtime <- tempmed[order(tempmed["totalTime"]),]$totalTime
      medconv <- data.frame(med1 = head(sortedtime, 1), med2 = tail(sortedtime, 1))
      medconv$diff <- difftime(medconv$med2,medconv$med1, units = "hours")
      if (medconv$diff %>% is_empty()) {
        break
      }
      medconv$med <- rep(y)
      medconv$admittolast <- nsti_new[nsti_new$Patient == i,]$Minutes.from
      medconv$debtomed <- difftime(medconv$med2, debridedate, units = "hours")
      medconv$patient <- i
      
      medsdf = rbind(medsdf, subset(medconv, select = c(diff, med, admittolast, patient, debtomed)))
    }
  }
} 
```


Vizualization towards understadning the new debride to med calculations 

```{r}
# finding out the outliers 
ggplot(data = melt(medsdf %>% subset(admittolast <12500) %>% subset(diff < 500) %>% subset(debtomed < 250)), aes(x=variable, y=value)) + 
  geom_boxplot() +
  facet_wrap(.~ variable, scale = "free")


```

```{r fig.height = 10, fig.width = 15}

ggplot(data = medsdf , aes( x = admittolast)) +
  geom_histogram() +
  scale_colour_gradientn(colours = terrain.colors(10)) + 
  facet_wrap(.~ med)
ggplot(data = medsdf , aes( x = diff)) +
  geom_histogram() +
  scale_colour_gradientn(colours = terrain.colors(10)) + 
  facet_wrap(.~ med)

ggplot(data = medsdf , aes( x = debtomed)) +
  geom_histogram() +
  scale_colour_gradientn(colours = terrain.colors(10)) + 
  facet_wrap(.~ med)

```



```{r fig.height = 20, fig.width = 15}
test = medsdf %>% subset(admittolast <12500) %>% subset(diff < 500) %>% subset(debtomed < 250)

ggplot(data = medsdf, aes(y = diff, x = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  #facet_wrap(med~. ) +
  labs( x = "Admit to last debridement", y= "Difference from last to first med") +
  geom_text(aes(label=ifelse((admittolast>4*IQR(admittolast) | diff > 4*IQR(diff)),patient,"")), hjust=1.1)


```

```{r warning= FALSE}
medwane <- data.frame(patient = integer())
medwanetreedf <- data.frame(patient = nsti_new$Patient)

for (i in nsti_new$Patient){
  if ((which(nstimeds_new$study_ID == i) %>% is_empty()) != TRUE){
    temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
    temptime <- temp[order(temp["totalTime"]),]
    theDate <- head(temptime$totalTime, 1)
    end <- tail(temptime$totalTime, 1)
    daycount = 0
    while (theDate <= end){
      daycount = daycount + 1
      tempmed <- temptime %>% subset(totalTime >= theDate) %>% subset(totalTime <= theDate + days(1))
      tempmednum = data.frame(unimed = length(unique(tempmed$Meds)), patient = i, daycount = daycount)
      tempmednum$meds = list(unique(tempmed$Meds))
      medwanetreedf[which(medwanetreedf$patient == i),]$daycount <- length(unique(tempmed$Meds))
      medwane = rbind(medwane, tempmednum)
      
      theDate <- theDate + days(1)
    }
  }
} 



head(medwane$meds[1])

```



```{r fig.width= 20}

#data tree w/ sankey diagram

#nsti_tree <- as.data.frame()




#data.tree
head(medwane)

medwanetrans <- data.frame(patient = integer())

for (i in unique(medwane$patient)){
  temp <- medwane[medwane$patient == i,]
  tempdf <- data.frame(patient = i)
  tempdf$unimed <- list(temp$unimed)
  medwanetrans <- rbind(medwanetrans, tempdf)
}

medwanetrans$pathString <- paste("Meds A day",sapply(medwanetrans$unimed, paste, collapse = "/"), medwanetrans$patient, sep = "/")

medwanetrans$medcount <- sapply(medwanetrans$unimed, length)
medwanetrans %>% subset(medwanetrans$medcount <= 10)

testTree <- as.Node(medwanetrans %>% subset(medwanetrans$medcount <= 10))

print(testTree, limit = 200)
png("test.png", width = 600, height = 600)
plot(testTree)

ToDiagrammeRGraph(testTree)

# Sankey Diagram

head(medwane$meds[[3]])

p <- plot_ly(
    type = "sankey",
    orientation = "h",

    node = list(
      label = c("A1", "A2", "B1", "B2", "C1", "C2"),
      color = c("blue", "blue", "blue", "blue", "blue", "blue"),
      pad = 15,
      thickness = 20,
      line = list(
        color = "black",
        width = 0.5
      )
    ),

    link = list(
      source = c(0,1,0,2,3,3),
      target = c(2,3,3,4,4,5),
      value =  c(8,4,2,8,4,2)
    )
  ) %>% 
  layout(
    title = "Basic Sankey Diagram",
    font = list(
      size = 10
    )
)

```


```{r fig.height= 7, fig.width = 15}
ggplot(data = medwane, aes(x = daycount, y = unimed)) +
  geom_jitter()
ggplot(data = medwane %>% subset(daycount < 50), aes(x= daycount)) +
  geom_density()

#looks nice but pointless
ggplot(data = medwane %>% subset(daycount < 50), aes(x= daycount, y = unimed)) +
  geom_bar(stat = "identity",aes(fill = patient)) +
  theme(legend.position = "none") 

ggplot(data = medwane %>% subset(daycount < 30), aes(y = unimed, x =daycount)) + 
  geom_boxplot() +
  scale_y_continuous(breaks=c(0:10)) +
  facet_grid(.~daycount, scale = "free")

ggplot(data = medwane, aes(y = unimed, x =daycount)) + 
  #geom_line() +
  scale_y_continuous(breaks=c(0:10))+
  theme(legend.position = "none") +
  geom_smooth(method = 'loess', se = FALSE)
  
```


```{r}
#Creating a data structure that categorizes medication, time and orders them within a list in a list 
# in the nsti data as it has the actual length of patients 
nsti$medsort <- list("")

for (i in nsti$Patient){
  temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
  meds = strsplit(paste(unique(temp$Meds)), " ")
  medsdf = list()
  for (y in meds){
    tempmed <- temp[temp$Meds == y,]
    medsdf[[y]] <- tempmed[order(tempmed["totalTime"]),]$totalTime
  }
  nsti[nsti$Patient == i,]$medsort <- list(medsdf)
} 
```



```{r}
#head(nsti$medsort)
```

```{r}
#ggplot(data = medsdf, aes(x = as.numeric(row.names(medsdf)),y = hours)) + 
#  geom_step(direction = "hv")
  
```

```{r}
#ggplot(data = tail(medsdf,-3), aes(x = as.numeric(row.names(tail(medsdf,-3))),y = hours)) + 
#  geom_step(direction = "hv")
```


```{r}
# graphing all of the points from patients 

medsdf = data.frame(order = integer(), med = character(), diff = character())

for (i in nsti_new$Patient){
  temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
  meds = strsplit(paste(unique(temp$Meds)), " ")
  for (y in meds){
    tempmed <- temp[temp$Meds == y,]
    if (nrow(tempmed) >1){
      sortedtime <- tempmed[order(tempmed["totalTime"]),]$totalTime
      medconv <- data.frame(med1 = head(sortedtime, -1), med2 = tail(sortedtime, -1))
      medconv$diff <- difftime(medconv$med2,medconv$med1, units = "hours")
      medconv <- medconv %>% subset(diff > 0) # removes any where that the difference in time is a zero 
      if (medconv$diff %>% is_empty()) {
        break
      }
      medconv$med <- rep(y)
      medconv$order <- as.numeric(row.names(medconv))
      medconv$admittolast <- nsti_new[nsti_new$Patient == i,]$Minutes.from
      medconv$patient <- i
      medsdf = rbind(medsdf, subset(medconv, select = c(diff, med,order, admittolast, patient)))
    }
  }
} 

```

```{r}
medconv$diff %>% is_empty()
```

```{r fig.height = 20, fig.width = 15}
test = medsdf %>% subset(diff < 30) %>% subset(admittolast <40000)
ggplot(data = test[test$med == "VANC",], aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change", title = "VANC")
ggplot(data = test[test$med == "CLIN",], aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change", title = "CLIN")
ggplot(data = test[test$med == "PCNG",], aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change", title = "PCNG")
```



Seems like half of the antibiotics dont have many datapoints so it is better to elimate those 

*No to almost no data available*
- ANTIBIOT,HEP, NOREPI, PCC, GENT 

*Limited amount of data*
- CIPR, LEVO, METR, PIPE, SOFA

*A lot of data*
- CLIN, MERO, PCNG, VANC

```{r fig.height = 20, fig.width = 15}

ggplot(data = test, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")


```

```{r  fig.height = 20, fig.width = 15}
#ANTIBIOT,HEP, NOREPI, PCC, GENT 
lowdatamed = test[which(test$med == "ANTIBIOT"| test$med == "NOREPI" |test$med == "PCC" |test$med == "GENT" ),]
ggplot(data = lowdatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")

meddatamed = test[which(test$med == "CIPR"| test$med == "LEVO" |test$med == "METR" |test$med == "PIPE" |test$med == "SOFA"),]

ggplot(data = meddatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")

highdatamed = test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "PCNG" |test$med == "VANC" ),]

ggplot(data = highdatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")


```

```{r fig.height = 20, fig.width = 15}
highdatamed = test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "VANC" ),]

ggplot(data = highdatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")

```


```{r fig.height = 13, fig.width = 15}
#filteredtest <- test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "VANC"|test$med == "CIPR"| test$med == "LEVO" |test$med == "METR" |test$med == "PIPE" |test$med == "SOFA"),]

#ggplot(data = filteredtest, aes(x = admittolast, fill = med)) +
#  geom_histogram(position = "fill")

#ggplot(data = filteredtest, aes(x = admittolast, fill = med)) +
#  geom_histogram(position = "stack")
``` 
```{r fig.height = 20, fig.width = 15}

#highdatamed = test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "PCNG" |test$med == "VANC" ),]
#ggplot(data = test[which(test$patient == 1),], aes(x = order, y = diff, col = patient)) +
#  geom_line() +
##  facet_grid(med~. )+
#  theme(legend.position = "none") 

```

```{r}
#CPPROC2014 %>% subset(PROC == 9670)
```


