---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: true
    themed: united 
  pdf_document: default
---
```{r echo = FALSE, message=FALSE}
library(plyr); library(dplyr) # data manipulation
library(tidyverse) 
library(ggplot2) # data visualization
library(stats)

require(data.table) # data visualization
library(tidyr)
library(chron)
library(lubridate)
library(data.tree)
library(plotly)
library(d3r)
library(htmltools)
#library(rhtmlSankeyTree)

# Importing dataset
nsti <- data.frame(fread("NSTI_for_KL.csv", header = TRUE))
nsti_debrid <- data.frame(fread("NSTI_debride_for_KL.csv", header = TRUE))
nsti_Meds <- data.frame(fread("NSTI_meds_for_KL.csv",header = TRUE))
NSTI_labs <- data.frame(fread("NSTI_WBC_updated_for_KL.csv", header = TRUE))
```

# Overview

# File Breakdown

*nsti* : contains demographic data, cost (inaccurate), insurance, etc on all patients

*NSTI_meds* contains antibiotics taken over the course of the patients stay 

*nsti_debrid* contains all of the debridement events and reconstruction events

*NSTI_labs* contains WBC on debridement events (Currently inaccurate)

# Purpose

To understand/quantify the time between last debridement and last medication change 
 - Why?
 
# Future goals 

**WBC association** To see if the WBC can be associated and tracked onside the medication changes 

**"Total Cost"** Ask: How is cost assocaited with the medication changes   

**Goal** is to determine whether there are characteristics that predict who will cost the most (top quartile).


# Overview on features

**Features** (nsti: 78 variables)

**Numerical**

- Patient, Age, Race
- Discharge Date
- Outcome?? (categorical)
- Admit date (x /y??)
- ICU los??, ICU hours (num)
- Hosp los?? (num)
- Vent Days(num) 
- DC dispo (categorical)
- Mech of infection (categorical)

**Categorical**

- Comorbid codes (Categorical seperated by ";")
- co.morbids (numerical)
- location code 1,2 (categorical, only on some patients)
- ICD 10 code & description / ICD 10 2 missing?? 
- Region (categorical)
- debirdment count (numerical - int)
- direct cost days? (only on some patients)
- direct/indirect cost/total cost (numerical)
- direct cost index / pb hmc (direct/inndirect/total cost) / pb uwp gross charges / cost allocation (only on some patients )
- Vent free days (numerical)
- insurance & type (categorical)

**Binary**

- Transfer (binary)
- **transfer** duplicate 
- Debridement
- Ards, arf cauti, cdiff, clabsi, cva, cpr, decub, dvt, unplanned (ett & or), mi, pe, sepsis, vap, withdrawl, bleeding, chf, cirr, crf, cva, dm, dementia, drug abuse, etoh abuse, htn, MI, resp, smoker, amputation
- death 
- is female
- highest quartile cost 
- public/private/uninsured insurance
- other??

```{r}
# stats of the inital files 
summary(nsti)
head(nsti)
```

```{r}
 knitr::knit_exit()
```

```{r}
#removing the duplicate transfer binary 
nsti <- subset(nsti, select = -c(TRANSFER,OUTCOME, isFemale))
```

# Data Cleaning 

**Nsti**
```{r}
# Extracting numerical identifier
nsti["Patient"] <- lapply(nsti["Patient"], function(x) str_sub(x, 1,-6))

#Splitting features that are bound by semi colons into a list
nsti["CoMorbid.Codes"] <- lapply(nsti["CoMorbid.Codes"], function(x) strsplit(x, ";"))
nsti["Insure"] <- lapply(nsti["Insure"], function(x) strsplit(x, ";"))

#converting character to date data format
dates = c("Discharge", "Admit.x", "Admit.y")
nsti[dates] <- lapply(nsti[dates], function(x) as.Date(x, "%m/%d/%Y"))

#Converting categorical features to factor
cols <- c("SEX", "RACE", "DC.DISPO", "MECHANISM.OF.INFECTION", "LOCATION.CODE.1", "LOCATION.CODE.2", "ICD.10..1.DESCRIPTION", "REGION",
          "Insure_type", "ICD.10.CODE..1")
nsti[cols] <- lapply(nsti[cols], as.factor)

#replacing NOT in race to NA
nsti$RACE[ nsti$RACE == "NOT"] <- NA
```

Region is weird case in which is can have more than one region. Not sure how we want to address this.
Issue with patient 179*NSTI or V1 (70) which has a co.morbids value of asthma 

```{r}
nsti[nsti$V1 == 70,]
```

**Debrid**
Changing the date features that were typed under character to actual date types as posicit as well as features that should be factors as well 

```{r}
#changing to date type
dates = c("ADMIT.DATE", "DEBRIDE.1.START.DATE", "DEB.2.DATE","DEB3.DATE", "DEB4.DATE", "REC1.DATE", "REC2.DATE", "REC3.DATE", "REC4.DATE", "DC.Date")
nsti_debrid[dates] <- lapply(nsti_debrid[dates], function(x) as.Date(x, "%m/%d/%Y"))

#changing to factors 
cols <- c("DEB1.CPT", "DEB2.CPT", "DEB3.CPT", "DEB4.CPT", "REC1CPT", "REC1.TOTAL", "REC1.EXP", "REC1.FLAP",
          "REC2.CPT", "REC2.EXP","REC2.FLAP", "Transfer")
nsti_debrid[cols] <- lapply(nsti_debrid[cols], as.factor)
```

**Meds**
Converting the features to factors 

```{r}
cols <- c("Meds", "Med.Location")
nsti_Meds[cols] <- lapply(nsti_Meds[cols], as.factor)
```

Structuring the time data in medication
```{r}
#creating a new dataframe with only these medications 
nstimeds_new <- data.frame(nsti_Meds[nsti_Meds["Meds"] != c("DOBU", "ENOX", "EPINEP", "NOPRESS", "STERIOD", "VASO", "WARF", 
                                                        "ANTIBIOT", "DOP", "HEP", "IVIG", "NOREPI", "PCC", "SOFA"),])
#removing med location
nstimeds_new <- subset(nstimeds_new, select = -c(Med.Location))

#removing entries that have a NOT date/time or UNK might go back and change if there is an alternative route 
nstimeds_new <- nstimeds_new[nstimeds_new["Med.Start.Date"] != "NOT" & nstimeds_new["Med.Start.Date"] != "UNK" & nstimeds_new["Med.Start.Date"] != "",]

#converting NOT to 0.00 Not a good system need to revise if we are using med location 
nstimeds_new[nstimeds_new == "NOT"] <- "0:00"
nstimeds_new[nstimeds_new == ""]  <- "0:00"
nstimeds_new[nstimeds_new == "UNK"]   <- "0:00"

# removes all na. Need to reassess later for 
nstimeds_new = nstimeds_new[complete.cases(nstimeds_new),]

unlist(unique(nsti_Meds["Meds"]))
```

```{r}
#Converting time and date to a new feature with both 
nstimeds_new$totalTime <- strptime(paste(nstimeds_new$Med.Start.Date,nstimeds_new$Med.Start.Time, sep = " "),"%m/%d/%Y %H:%M")
```

```{r}
#merging datasets with medication data
nsti_new <- merge(nsti,nsti_debrid, by.x = "Patient", by.y = "study_ID")
nsti_new <- nsti_new[nsti_new$Minutes.from > 0,]
nsti_new <- nsti_new[complete.cases(nsti_new$Minutes.from),]
#nsti_med_time <- subset(nsti_new, select = c(Patient, Admit.x, medsort,Minutes.from))
```

Features I need to create:
- Admittolast: Time between admission and last debridement
     - minutes from admit to last deb
- Diff: Total time each patient received each antibiotic (should be the difference between the first med start date/time until the last med start date/time for each patient--ignore all time points between first and last administration)
     - last medication to first medication
- Debtomed:  Time between last debridement and last med start date/time for each antibiotic
     - hours from last med to last deb 

```{r}
medsdf = data.frame(patient = integer(), med = character(), diff = character()) # empty df

# for loop that creates the features 
for (i in nsti_new$Patient){
  temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
  meds = strsplit(paste(unique(temp$Meds)), " ")
  debridepatient = nsti_debrid %>% subset(study_ID == i)
  #creating the debride time then adding the time to last 
  debridedate = strptime(paste(debridepatient$DEBRIDE.1.START.DATE,debridepatient$DEBRIDE.1.START.TIME, sep = " "),"%Y-%m-%d %H:%M") +
                debridepatient$Minutes.from.1st.Deb.to.last*60
  for (y in meds){
    tempmed <- temp[temp$Meds == y,]
    if (nrow(tempmed) >1){
      sortedtime <- tempmed[order(tempmed["totalTime"]),]$totalTime
      medconv <- data.frame(med1 = head(sortedtime, 1), med2 = tail(sortedtime, 1))
      medconv$diff <- difftime(medconv$med2,medconv$med1, units = "hours")
      if (medconv$diff %>% is_empty()) {
        break
      }
      medconv$med <- rep(y)
      medconv$admittolast <- nsti_new[nsti_new$Patient == i,]$Minutes.from
      medconv$debtomed <- difftime(medconv$med2, debridedate, units = "hours")
      medconv$patient <- i
      
      medsdf = rbind(medsdf, subset(medconv, select = c(diff, med, admittolast, patient, debtomed)))
    }
  }
} 

# debtomed tuning, getting the maximium time 
temp = medsdf %>% select(patient, debtomed)
tempmedtodf = data.frame("patient" = character(), "debtomed" = integer())

for (i in unique(temp$patient)){
  temppatient = max((temp %>% subset(patient == i))$debtomed)
  tempmedtodf = rbind(tempmedtodf, data.frame("patient" = i, "debtomed" = temppatient))
}

tempmedtodf
```

Vizualization towards understadning the new debride to med calculations 

```{r}
# finding out the outliers 
ggplot(data = melt(medsdf %>% subset(admittolast <12500) %>% subset(diff < 500) %>% subset(debtomed < 250)), aes(x=variable, y=value)) + 
  geom_boxplot() +
  facet_wrap(.~ variable, scale = "free")

ggplot(data = melt(tempmedtodf %>% subset(debtomed >0) %>% subset(debtomed < 500)), aes(x=variable, y=value)) + 
  geom_boxplot() 

tempmedtodf %>% subset(debtomed < 0)
```

```{r fig.height = 10, fig.width = 15}
# more visualizations towards understanding the graph
ggplot(data = medsdf , aes( x = admittolast)) +
  geom_histogram() +
  scale_colour_gradientn(colours = terrain.colors(10)) + 
  facet_wrap(.~ med)
ggplot(data = medsdf , aes( x = diff)) +
  geom_histogram() +
  scale_colour_gradientn(colours = terrain.colors(10)) + 
  facet_wrap(.~ med)

ggplot(data = medsdf , aes( x = debtomed)) +
  geom_histogram() +
  scale_colour_gradientn(colours = terrain.colors(10)) + 
  facet_wrap(.~ med)

```



```{r fig.height = 20, fig.width = 15}
filteroutlier = medsdf %>% subset(admittolast <12500) %>% subset(diff < 500) %>% subset(debtomed < 250)

ggplot(data = medsdf, aes(y = diff, x = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  #facet_wrap(med~. ) +
  labs( x = "Admit to last debridement", y= "Difference from last to first med") +
  geom_text(aes(label=ifelse((admittolast>4*IQR(admittolast) | diff > 4*IQR(diff)),patient,"")), hjust=1.1)
```

Starting to do the survival curve data and understanding which meds a patient is taking for each day from there first 

```{r warning= FALSE}
# creates the df "medwane" such that it says what kind of medication each patient is taking on each day 

#      med   /    patient     / daycount 

medwane <- data.frame(patient = integer())
medwanetreedf <- data.frame(patient = nsti_new$Patient)

for (i in nsti_new$Patient){
  if ((which(nstimeds_new$study_ID == i) %>% is_empty()) != TRUE){
    temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
    temptime <- temp[order(temp["totalTime"]),]
    theDate <- head(temptime$totalTime, 1)
    end <- tail(temptime$totalTime, 1)
    daycount = 0
    while (theDate <= end){
      daycount = daycount + 1
      tempmed <- temptime %>% subset(totalTime >= theDate) %>% subset(totalTime <= theDate + days(1))
      tempmednum = data.frame(unimed = length(unique(tempmed$Meds)), patient = i, daycount = daycount)
      tempmednum$meds = list(unique(tempmed$Meds))
      medwanetreedf[which(medwanetreedf$patient == i),]$daycount <- length(unique(tempmed$Meds))
      medwane = rbind(medwane, tempmednum)
      theDate <- theDate + days(1)
    }
  }
}
```


```{r fig.width= 20}

#data tree w/ sankey diagram

#nsti_tree <- as.data.frame()

#data.tree
head(medwane)

medwaneuni <- medwane

medwanetrans <- data.frame(patient = integer(), medcount = integer())


#adding a limit for sankey diagram not sure if I like it 
medlimitnum = 28

for (i in unique(medwaneuni$patient)){
  temp <- medwane[medwaneuni$patient == i,]
  tempdf <- data.frame(patient = i)
  #   tempdf$unimed <- list(temp$unimed)
  tempdf$unimed <- list(replace(temp$unimed, temp$unimed> 5, 6))
  tempdf$medcount <- length(tempdf$unimed[[1]])
  for (j in (length(tempdf$unimed[[1]]) +1 ):medlimitnum){
    tempdf$unimed[[1]][j] = 0
  }
  medwanetrans <- rbind(medwanetrans, tempdf)
}

j
i = 2
length(medwanetrans$unimed[[98]])
medwanetrans$unimed[[1]]
tempdf$unimed[[1]]
t
tempdf
```

```{r fig.width= 10, fig.height= 10}
#understanding outlier patients 

summary(medwanetrans$medcount)

# patients with more than 100 
medwanetrans %>% subset(medcount >= 100)

# patients with 50 - 100
medwanetrans %>% subset(medcount >= 50 & medcount < 100) 

# patients with 25-50
medwanetrans %>% subset(medcount >= 25 & medcount < 50) 

# patients with 20- 25
medwanetrans %>% subset(medcount >= 20 & medcount < 25) 

tempmedwane = medwanetrans %>% subset(medcount < 28)
ggplot(data = tempmedwane, aes( y=medcount)) + 
  geom_boxplot() 

tempmedwane =  data.frame("first" = sapply(medwanetrans$unimed, function(x) as.integer(x[[1]])))

ggplot(data = tempmedwane, aes( x=first)) + 
  geom_bar() 

```

```{r}
# for the basic tree diagram. not usinig it right now 
#medwanetrans$pathString <- paste("Meds A day",sapply(medwanetrans$unimed, paste, collapse = "/"), medwanetrans$patient, sep = "/")

#medwanetrans$medcount <- sapply(medwanetrans$unimed, length)
#medwanetrans %>% subset(medwanetrans$medcount <= 10)

#testTree <- as.Node(medwanetrans %>% subset(medwanetrans$medcount <= 10))

#print(testTree, limit = 200)
#png("test.png", width = 600, height = 600)
#plot(testTree)

#ToDiagrammeRGraph(testTree)
```

```{r}
# Sankey Diagram

sankeynode <- data.frame("name" = character(), "node" = character())

medwanesankey <- data.frame('source' = character(), 'target' = character(), 'value' = integer())

for (i in (medwanetrans %>% subset(medcount <= 28))$patient){
  temp = (medwanetrans %>% subset(patient == i))$unimed[[1]]
  if (length(temp)> 1){
    for (j in 2:length(temp)-1){
      sourcetemp = paste(j,substr("ABCDEFGHJIKLMNOP", temp[j], temp[j]))
      targettemp = paste(j+1,substr("ABCDEFGHJIKLMNOP", temp[j+1], temp[j+1]))
        if (!sourcetemp %in% sankeynode$node){
          sankeynode <- rbind(sankeynode, data.frame("name" = paste("Day ",j, ":", temp[j], sep = ""), "node" = sourcetemp))
        }
        if (!targettemp %in% sankeynode$node){
          sankeynode <- rbind(sankeynode, data.frame("name" = paste("Day ",j+1, ":", temp[j+1], sep = ""), "node" = targettemp))
        }
      tempdf <- data.frame('source' = which(sankeynode$node == sourcetemp), 'target' = which(sankeynode$node == targettemp))
      if (nrow(merge( tempdf, medwanesankey)) < 1) {
        tempdf$value <- 1
        medwanesankey <- rbind(medwanesankey, tempdf)
      } else {
        medwanesankey[which(medwanesankey$source == tempdf$source & medwanesankey$target == tempdf$target),]$value =  
        medwanesankey[which(medwanesankey$source == tempdf$source & medwanesankey$target == tempdf$target),]$value + 1
      }
    }
  }
}


library(networkD3)
nodes = data.frame("name" = sankeynode$name)
links = medwanesankey[with(medwanesankey,order(source,target)),]
links$source = links$source -1
links$target = links$target -1

p <- plot_ly(
    type = "sankey",
    domain = c(
      x =  c(0,1),
      y =  c(0,1)
    ),
    orientation = "h",
    arrangement = "perpendicular",
    node = list(
      label = nodes$name,
      pad = 5,
      thickness = 5,
      line = list(
        color = "black",
        width = 0.5
      )
    ),
    link = list(
      source = links$source,
      target = links$target,
      value =  links$value,
      label =  nodes$name
    )
) %>%
  layout(
    font = list( size = 15),
    xaxis = list(showgrid = F, zeroline = F),
    yaxis = list(showgrid = F, zeroline = F),
    width = 1500, height = 900
  )
p

#chart_link = api_create(p, filename="sizing-1")
#chart_link
```

```{r fig.height= 15, fig.width = 15}
#survival curve 

library(ggfortify)
library(survminer)
library(survival)
head(medwane)

medwane <- data.frame(patient = integer())

#This does not work with the survival package. Use the medwane admit or the medwanenew 
for (i in nsti_new$Patient){
  if ((which(nstimeds_new$study_ID == i) %>% is_empty()) != TRUE){
    temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
    temptime <- temp[order(temp["totalTime"]),]
    theDate <- head(temptime$totalTime, 1)
    end <- tail(temptime$totalTime, 1)
    daycount = 0
    while (theDate <= end){
      daycount = daycount + 1
      tempmed <- temptime %>% subset(totalTime >= theDate) %>% subset(totalTime <= theDate + days(1))
      if (length(tempmed$Meds) != 0){
        tempmednum <- data.frame("med" = unlist(unique(tempmed$Meds)), patient = as.integer(i), daycount = as.integer(daycount))
      } else {
        tempmednum <- data.frame("med" = c(""), patient = as.integer(i), daycount = as.integer(daycount))
      }
      medwane = rbind(medwane, tempmednum)
      
      theDate <- theDate + days(1)
    }
  }
}

survtest <- dcast(medwane, patient + daycount ~ med, fun.aggregate = length, value.var = "med")

medwanenew <- data.frame(patient = integer(), med = character(), status = integer(), daycount = integer())
# resctructuring of data for better survival curve 
for (i in 2:nrow(survtest)){
  temp = survtest[i,] %>% select( -c(patient, daycount, Var.3))
  previous = survtest[(i-1),] %>% select( -c(patient, daycount, Var.3))
  for (j in 1:length(temp)){
    if (temp[j] == 0 & previous[j] == 1){
      medwanenew <- rbind(medwanenew, data.frame(patient = survtest[i,]$patient, med = names(temp[j]), status = 1,daycount = survtest[i,]$daycount))
    } 
  }
}
```

```{r}
# survival curve such that there are no gaps
# TRUE = the continuous patients 
# FALSE = the raw dataset 
if (TRUE){
  admitdf = nstimeds_new[!nstimeds_new$study_ID %in% unique((medwane %>% subset(med == ""))$patient),] 
} else {
  admitdf = nstimedds_new
}

medwane[medwane$patient %in% unique((medwane %>% subset(med == ""))$patient),]

#116, 120, 126, 131, 139 & 141 & 143(had one 1 day gap )
```


```{r}
#editing survival curve for admission
medwaneadmit <- data.frame(patient = integer(), status = integer(), daycount = double(), debridecount = integer(), region = character())
for (i in nsti_new$Patient){
  if ((which(admitdf$study_ID == i) %>% is_empty()) != TRUE){
    temp <- admitdf[which(admitdf$study_ID == i,),]
    temptime <- temp[order(temp["totalTime"]),]
    admission <- strptime((nsti_new %>% subset(Patient == i))$ADMIT.DATE, "%Y-%m-%d")
    end <- tail(temptime,1)$totalTime
    nsti_temp <- nsti_new %>% subset(Patient == i)
    discharge <- strptime(nsti_temp$Discharge,"%Y-%m-%d")
    debridect <- nsti_temp$DEBRIDE.COUNT - nsti_temp$Debridement.at.REF
    if (discharge > end){
       tempstatus = 1
       tempdaycount = difftime(end,admission)
    } else {
       tempstatus = 0
       tempdaycount = difftime(discharge,admission)
    }
    medwaneadmit <- rbind(medwaneadmit, data.frame(patient = i, status = tempstatus,daycount = tempdaycount, debridecount = debridect, 
                                                   region = as.character(nsti_temp$REGION)))
  }
}


```

```{r fig.width= 10, fig.height= 10}
#chances the df to be a better format. Works only on medwane

#filtersurv <- survtest %>% subset(daycount <200)
#filtersurv <- survtest[! survtest$patient %in% c(unique((survtest %>% subset(daycount > 100))$patient)),]
#filtersurv <- filtersurv[!filtersurv$patient %in% c(74,134,149,15,734),]
#filtersurv <- survtest[ survtest$patient %in% c(unique(survtest %>% subset(daycount == 1) %>% subset(CLIN == 1))$patient),]

#survival Curve 
fit <- surv_fit(Surv( time = daycount, event= status) ~region, data = medwaneadmit, conf.type = "log-log") 
#autoplot(fit)
ggsurvplot(fit, data = medwaneadmit, risk.table = TRUE)
```



```{r}
#WBC

NSTI_labs %>% subset(Observation == "WBC") %>% subset(Patient == 99)
test = (nstimeds_new %>% subset(study_ID == 99))
tail(test[order(test["totalTime"]),],1)

temp[order(temp["totalTime"]),]

medwbc <- data.frame(patient = integer(), wbc = integer(), antibiotic = integer(), diff = double())
difmedwbc <- data.frame(patient = integer(), wbc = integer(), antibiotic = character(), diff = double())
for (i in nsti_new$Patient){
  if ((which(nstimeds_new$study_ID == i) %>% is_empty()) != TRUE){
    temp <- nstimeds_new %>% subset(study_ID == i)
    tempend <- tail(temp[order(temp["totalTime"]),],1)$totalTime
    wbc <- NSTI_labs %>% subset(Lab.Code == "WBC") %>% subset(TRACKING.NO == i)
    wbc$TotalTime <- strptime(paste(wbc$Lab.Date,wbc$Lab.Time, sep = " "),"%m/%d/%Y %H:%M")
    wbcend <- max(wbc$TotalTime)
    
    medwbc <- rbind(medwbc, data.frame(patient = i, wbc = wbcend,antibiotic = tempend, diff = difftime(wbcend,tempend, units = "hours")))
  }
}

# the count of the time differencec between wbc lab date and the date of the last medication 
count((medwbc %>% subset(diff >= 1 | diff <= -1)))

# 102, 106, 12, 122
# CLIN, VANC, MERO  | CLIN, PCNG | CLIN, PCNG, VANC | CLINC PIPE
# wbc and last antibiotic date don't have any matching 
NSTI_labs %>% subset(Lab.Code == "WBC")

NSTI_labs$admittolab <- difftime(strptime(paste(NSTI_labs$Lab.Date,NSTI_labs$Lab.Time, sep = " "),"%m/%d/%Y %H:%M"), strptime(NSTI_labs$ADMIT.DATE, "%m/%d/%Y"))

NSTI_labs %>% subset(Lab.Code =="WBC")

#always close to the start date never the end date

```

```{r}
NSTI_labs %>% subset(Observation == "WBC") %>% subset(Patient == 817)
test = (nstimeds_new %>% subset(study_ID == 817))
tail(test[order(test["totalTime"]),],1)
```



#```{r fig.height= 7, fig.width = 15}
ggplot(data = medwane, aes(x = daycount, y = unimed)) +
  geom_jitter()
ggplot(data = medwane %>% subset(daycount < 50), aes(x= daycount)) +
  geom_density()

#looks nice but pointless
ggplot(data = medwane %>% subset(daycount < 50), aes(x= daycount, y = unimed)) +
  geom_bar(stat = "identity",aes(fill = patient)) +
  theme(legend.position = "none") 

ggplot(data = medwane %>% subset(daycount < 30), aes(y = unimed, x =daycount)) + 
  geom_boxplot() +
  scale_y_continuous(breaks=c(0:10)) +
  facet_grid(.~daycount, scale = "free")

ggplot(data = medwane, aes(y = unimed, x =daycount)) + 
  #geom_line() +
  scale_y_continuous(breaks=c(0:10))+
  theme(legend.position = "none") +
  geom_smooth(method = 'loess', se = FALSE)
  
#```


#```{r}
#Creating a data structure that categorizes medication, time and orders them within a list in a list 
# in the nsti data as it has the actual length of patients 
nsti$medsort <- list("")

for (i in nsti$Patient){
  temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
  meds = strsplit(paste(unique(temp$Meds)), " ")
  medsdf = list()
  for (y in meds){
    tempmed <- temp[temp$Meds == y,]
    medsdf[[y]] <- tempmed[order(tempmed["totalTime"]),]$totalTime
  }
  nsti[nsti$Patient == i,]$medsort <- list(medsdf)
} 
#```

#```{r}
# graphing all of the points from patients 

medsdf = data.frame(order = integer(), med = character(), diff = character())

for (i in nsti_new$Patient){
  temp <- nstimeds_new[which(nstimeds_new$study_ID == i,),]
  meds = strsplit(paste(unique(temp$Meds)), " ")
  for (y in meds){
    tempmed <- temp[temp$Meds == y,]
    if (nrow(tempmed) >1){
      sortedtime <- tempmed[order(tempmed["totalTime"]),]$totalTime
      medconv <- data.frame(med1 = head(sortedtime, -1), med2 = tail(sortedtime, -1))
      medconv$diff <- difftime(medconv$med2,medconv$med1, units = "hours")
      medconv <- medconv %>% subset(diff > 0) # removes any where that the difference in time is a zero 
      if (medconv$diff %>% is_empty()) {
        break
      }
      medconv$med <- rep(y)
      medconv$order <- as.numeric(row.names(medconv))
      medconv$admittolast <- nsti_new[nsti_new$Patient == i,]$Minutes.from
      medconv$patient <- i
      medsdf = rbind(medsdf, subset(medconv, select = c(diff, med,order, admittolast, patient)))
    }
  }
} 

#```

#```{r}
medconv$diff %>% is_empty()
#```

#```{r fig.height = 20, fig.width = 15}
test = medsdf %>% subset(diff < 30) %>% subset(admittolast <40000)
ggplot(data = test[test$med == "VANC",], aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change", title = "VANC")
ggplot(data = test[test$med == "CLIN",], aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change", title = "CLIN")
ggplot(data = test[test$med == "PCNG",], aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change", title = "PCNG")
#```



Seems like half of the antibiotics dont have many datapoints so it is better to elimate those 

*No to almost no data available*
- ANTIBIOT,HEP, NOREPI, PCC, GENT 

*Limited amount of data*
- CIPR, LEVO, METR, PIPE, SOFA

*A lot of data*
- CLIN, MERO, PCNG, VANC

#```{r fig.height = 20, fig.width = 15}

ggplot(data = test, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")


#```

#```{r  fig.height = 20, fig.width = 15}
#ANTIBIOT,HEP, NOREPI, PCC, GENT 
lowdatamed = test[which(test$med == "ANTIBIOT"| test$med == "NOREPI" |test$med == "PCC" |test$med == "GENT" ),]
ggplot(data = lowdatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")

meddatamed = test[which(test$med == "CIPR"| test$med == "LEVO" |test$med == "METR" |test$med == "PIPE" |test$med == "SOFA"),]

ggplot(data = meddatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")

highdatamed = test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "PCNG" |test$med == "VANC" ),]

ggplot(data = highdatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")


#```

#```{r fig.height = 20, fig.width = 15}
highdatamed = test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "VANC" ),]

ggplot(data = highdatamed, aes(x = order, y = diff, colour = admittolast)) +
  geom_point() +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  facet_grid(med~. ) +
  labs(colour = "Admit to last DB", y = "Minutes between each medication change (Hours)", x = "Order of medication change")

#```


#```{r fig.height = 13, fig.width = 15}
#filteredtest <- test[which(test$med == "CLIN"| test$med == "MERO" |test$med == "VANC"|test$med == "CIPR"| test$med == "LEVO" |test$med == "METR" |test$med == "PIPE" |test$med == "SOFA"),]

#ggplot(data = filteredtest, aes(x = admittolast, fill = med)) +
#  geom_histogram(position = "fill")
ggplot(data = filteredtest, aes(x = admittolast, fill = med)) +
  geom_histogram(position = "stack")
#``` 
