---
title: "R Notebook"
output: html_notebook
---

*NSTI_for_KL* has all the demographic, cost, and insurance data.  
**"Total Cost"** is what we are interested in as outcome.  

**Goal** is to determine whether there are characteristics that predict who will cost the most (top quartile). 

*NSTI_meds_for_KL* has all the medications. 
- which patients got which antibiotics for how long
- when they were started, changed, and stopped in relationship to admission and last OR visit.

*NSTI_debride_for_KL* gives list of OR visits 



```{r}
library(tidyverse)
library(ggplot2)
library(stats)
library(plyr)
require(data.table)

#change to your directory when running
path <- "C:/Users/Kevin/Documents/GitHub/NSTI_harborview"
setwd(path)


# Importing dataset
nsti <- read.csv("~/GitHub/NSTI_harborview/NSTI_for_KL.csv")
#nsti_Meds <- fread("~/GitHub/NSTI_harborview/NSTI_meds_for_KL.csv",header = TRUE)

```

nsti: 78 variables
- Patient, Age, Race
- Discharge Date
- Outcome??
- Admit date


```{r}
head(nsti)
#summary(nsti_Meds)
```

